The MolSSI \qca Project: An open-source platform to compute, organize, and share quantum chemistry data

### 2020-05-18 main.tex
Fixed issues noted by L. Burns.  -TDC

The persistent use of \qcsk descriptions in \qcng simplifies writing software that uses CMS programs.
The input to all computations is a \qcsk specification document, such as an \texttt{AtomicInput} describing standard input to atomistic calculations (e.g., gradient evaluations).
Very few aspects of the inputs to \qcng are tied to the actual code which will fulfill the specified calculation, allowing users to efficiently perform computations with different quantum chemistry codes as scientific demands change.
The output from the codes is also returned in a standardized form, which simplifies databases and any software to analyze the outputs of a QC program.
Two examples: 1) a Hessian computed with Psi4\cite{Parrish:2017:3185} and NWChem\cite{Valiev:2010:1477} can be analyzed with the same software and
2) the geomeTRIC optimization package\cite{ping2016geometric, GH20:geometric} uses \qcng as an interface to different quantum chemistry packages so as to be agnostic the backend program.

@@

\begin{itemize}
     \item {\it Quantum Chemistry}:
     CFOUR,\cite{WEB19:cfour}
     Entos,\cite{Manby:2019:entos} 
     GAMESS,\cite{GAMESS:2005}
     Molpro,\cite{WEB20:molpro,MOLPRO-WIREs}
     NWChem,\cite{Valiev:2010:1477}
     Psi4,\cite{Parrish:2017:3185}
     Q-Chem,\cite{Shao:2015:184}
     Terachem,\cite{Ufimtsev:2009:2619}
     Turbomole\cite{Furche:2014:91}
     \item {\it Semi-empirical}:
     MOPAC\cite{WEB20:mopac}
     \item {\it ML Potential}:
     TorchANI\cite{GH20:torchani, Smith:2017:3192}
     \item {\it Molecular Mechanics}:
     RDKit,\cite{GH20:rdkit}
     OpenMM\cite{Eastman:2017:1}
     \item {\it Analytical Corrections}:
     DFTD3,\cite{GH20:dftd3, Grimme:2010:154104}
     MP2D\cite{GH20:mp2d, Rezac:2018:4711}
     \item {\it Geometry Optimizers}:
     geomeTRIC,\cite{GH20:geometric, Wang:2016:214108}
     PyBerny\cite{GH20:pyberny}
\end{itemize}

>>>>

The persistent use of \qcsk descriptions in \qcng simplifies writing software that uses CMS programs.
The input to all computations is a \qcsk specification document, such as an \texttt{AtomicInput} describing standard input to atomistic calculations (e.g., gradient evaluations).
Very few aspects of the inputs to \qcng are tied to the actual code which will fulfill the specified calculation, allowing users to efficiently perform computations with different quantum chemistry codes as scientific demands change.
The output from the codes is also returned in a standardized form, which simplifies databases and any software to analyze the outputs of a QC program.
Two examples: 1) a Hessian computed with Psi4\cite{Parrish:2017:3185,Smith:2020:psi4} and NWChem\cite{Apra:2020:nwchem} can be analyzed with the same software and
2) the geomeTRIC optimization package\cite{ping2016geometric, GH20:geometric} uses \qcng as an interface to different quantum chemistry packages so as to be agnostic the backend program.

@@

\begin{itemize}
     \item {\it Quantum Chemistry}:
     CFOUR,\cite{WEB19:cfour}
     Entos,\cite{Manby:2019:entos} 
     GAMESS,\cite{Barca:2020:gamess}
     Molpro,\cite{WEB20:molpro,MOLPRO-WIREs}
     NWChem,\cite{Apra:2020:nwchem}
     Psi4,\cite{Parrish:2017:3185,Smith:2020:psi4}
     Q-Chem,\cite{Shao:2015:184}
     Terachem,\cite{Ufimtsev:2009:2619}
     Turbomole\cite{Furche:2014:91}
     \item {\it Semi-empirical}:
     MOPAC\cite{WEB20:mopac}
     \item {\it ML Potential}:
     TorchANI\cite{GH20:torchani, Smith:2017:3192}
     \item {\it Molecular Mechanics}:
     RDKit,\cite{GH20:rdkit}
     OpenMM\cite{Eastman:2017:1}
     \item {\it Analytical Corrections}:
     DFTD3,\cite{GH20:dftd3, Grimme:2010:154104}
     MP2D\cite{GH20:mp2d, Rezac:2018:4711}
     \item {\it Geometry Optimizers}:
     geomeTRIC,\cite{GH20:geometric, Wang:2016:214108}
     PyBerny\cite{GH20:pyberny}
\end{itemize}
